\chapter{Conclusion}
\label{ch:conclusion}
A search for supersymmetry in scenarios with compressed mass spectra was performed using ATLAS data collected in 2015 and 2016 at $\sqrt(s)$ 13 TeV, corresponding to $36.1 fb^{-1}$. % \textcolor{red}{Motivate the searches for compressed electroweakinos and sleptons.}  
We searched for directly produced electroweakinos and sleptons in events containing two soft, oppositely signed and same flavored leptons and include missing transverse energy recoiling against hadronic initial state radiation.  Signal event characteristics are studied with Higgsino and slepton simplified models.  The directly produced electroweakinos and sleptons subsequently decay to their Standard Model partners and the lightest SUSY particle which is nearly degenerate in mass.  The energy given to the visible leptons is related to the mass-splitting between the neutral electroweakinos $\tilde\chi_2^0$ and $\tilde\chi_1^0$ or between the sleptons $\tilde\ell_{L,R}$ and the lightest neutral electroweakino $\tilde\chi_1^0$.  The relationship between lepton momentum and the mass-splittings provides discriminating variables unique to the electroweakino and slepton decays.  Electroweakinos signals are sensitive to the invariant mass of the dilepton system $m_{\ell\ell}$, and slepton signals are sensitive to the stransverse mass of the leptons and \met $m_{T2}^{100}$.  Inclusive and exclusive signal regions are binned in $m_{\ell\ell}$ for the search targeting electroweakino production, and in $m_{T2}^{100}$ for the search targeting sleptons.
 
The dominant backgrounds to signal event with soft leptons and \met are from jets faking leptons in the detector.  These are estimated with a data-driven fake factor technique and tested in a same-sign validation region that includes $ee+\mu e$ events in the electron channel, and $\mu\mu+e\mu$ events in the muon channel.  Irreducible backgrounds from $t\bar t$, $tW$, and $Z(\rightarrow\tau\tau)$+jets processes were estimated with Monte Carlo and normalized in data-driven control regions.  Irreducible diboson backgrounds were estimated with Monte Carlo and tested in a dedicated diboson validation region.  Low mass Drell Yan, Higgs, triboson, and multi-top backgrounds were estimated with Monte Carlo only.

Background only fits were performed on the CR-top and CR-tau to obtain background normalization parameters $\mu_{top} =0.72\pm0.13$ and $\mu_{\tau\tau}=1.02\pm0.09$, respectively.  The accuracy of the background prediction was tested in each of the validation regions and is consistently within $1.5~\sigma$ of the observed data.  Model independent upper limits were set at $95\%$ CL on the observed and expected upper limits on the number of signal events in the inclusive SRs were set with simultaneous fits in each SR and the CRs, assuming the background only hypothesis.  No significant excess in data over Standard Model background was found; therefore, results were consistent with Standard Model prediction. 

For model dependent interpretations, shape fits in $m_{\ell\ell}$ and $m_{T2}^{100}$ were performed.  These are full simultaneous fits over the exclusive, multi-binned SRs and the CRs including both signal and backgrounds predictions.  In the absence of significant excesses in data over background, result were interpreted as constraints on SUSY electroweakino and slepton models.  Higgsino models are excluded for next-to-lightest neutralino masses up to 130 GeV for mass splittings between 5 and 10 GeV. For mass splittings down to 3 GeV next-to-lightest neutralino masses are excluded up to 100 GeV.  For wino-bino simplified models, next-to-lightest neutralino masses are excluded up to 170 GeV for mass splittings above 10 GeV, and excluded up to 100 GeV for mass splittings down to 2.5 GeV.  For slepton simplified models, slepton masses are excluded up to 180 GeV for mass splittings down to 5 GeV. For mass splittings down to 1 GeV slepton masses are excluded up to 70 GeV.

Future prospects: more data and better triggers. better fake background estimates.  Way to model Drell-Yan and not cut away valuable low invariant mass phase-space.  Use of razor variables



