%% uctest.tex 11/3/94
%% Copyright (C) 1988-2004 Daniel Gildea, BBF, Ethan Munson.
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2003/12/01 or later.
%
% This work has the LPPL maintenance status "maintained".
% 
% The Current Maintainer of this work is Daniel Gildea.
\newcommand*{\ATLASLATEXPATH}{/Users/sheenaschier/Library/TexShop/texmf/tex/latex/atlaslatex-01-07-01/latex/}
\documentclass[11pt]{ucthesis}
\def\dsp{\def\baselinestretch{2.0}\large\normalsize}
\dsp
\usepackage{\ATLASLATEXPATH atlasphysics}
\usepackage{graphicx}     
\usepackage{amsmath}
\usepackage{accents}
\usepackage{tikz}	
\usepackage{placeins}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[font={small}]{caption}
\usepackage{lineno}
\usepackage{booktabs}
\linenumbers

\begin{document}

% Declarations for Front Matter

\title{Searches for Electroweak Production of Compressed Supersymmetry in Events with Soft Leptons, Missing Transverse Momentum, and a Hard Jet}
\author{Sheena Calie Schier}
\degreeyear{2018}
\degreemonth{June}
\degree{DOCTOR OF PHILOSOPHY}
\chair{Professor Abraham Seiden}
\committeememberone{Professor Jason Neilsen}
\committeemembertwo{Professor Michael Hance}
\numberofmembers{3} 
\deanlineone{Dean Tyrus Miller}
\deanlinetwo{Vice Provost and Dean of Graduate Studies}
\deanlinethree{}
\field{Physics}
\campus{Santa Cruz}

\begin{frontmatter}

\maketitle
\copyrightpage

\tableofcontents
\listoffigures
\listoftables

\makeatletter
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
%TODO: LINE NUMBERS

\begin{abstract}
Supersymmetry (SUSY) is an extension of the Standard Model that predicts a boson (fermion) partner for each fermion (boson) in the Standard Model. Weak-scale SUSY is attractive for reasons like improving gauge coupling unification, reducing fine-tuning in the Higgs sector and providing a dark matter candidate. In this thesis, I present a dedicated search for direct production of new, colorless, weak-scale states with a compressed mass spectra in final states characterized by soft visible decay products. This analysis uses $pp$ collisions at $\sqrt s$ = 13 TeV at the Large Hadron Collider and collected by the ATLAS experiment during 2015 and 2016 corresponding to 36.1 $\mathrm{fb}^{-1}$ of integrated luminosity. This analysis selects events with two soft electrons or muons and missing transverse momentum (\met{}) recoiling against hadronic initial state radiation. Backgrounds with two prompt leptons are estimated with Monte Carlo simulation, while reducible backgrounds are estimated with a mix of Monte Carlo and data-driven methods. Results are consistent with Standard Model expectations and used to put limits on compressed supersymmetric states.  Limits are extended on compressed electroweak SUSY model for the first time since LEP.

\end{abstract}

\begin{dedication}
\null\vfil
{\large
\begin{center}
To my father,\\\vspace{12pt}
Lecil Charles Schier,\\\vspace{12pt}
the person who taught me at the age of 7 that the grass in not green.
\end{center}}
\vfil\null
\end{dedication}


\begin{acknowledgements}
I want to ``thank'' my committee, without whose ridiculous demands, I
would have graduated so, so, very much faster.
\end{acknowledgements}

\end{frontmatter}

\include{introduction}
\part{Theoretical Motivation and Experimental Setup}
\include{theory}
\include{detector}
\part{Method}
\include{data}
\include{object}
%\iffalse
\include{regions}
\include{backgrounds}
\include{fakefactor}
\part{Analysis and Results}
\include{systematics}
\include{statanalysis}
\include{results}
\include{interpretations}
\include{conclusion}
%\fi

\nocite{*}
\bibliographystyle{plain}
\bibliography{uctest.bib}
%\printbibliography
\iffalse
\appendix
\include{apndx-A}
\include{apndx-B}
\include{apndx-C}
Ancillary material should be put in appendices, which appear after the
bibliography. 
\fi
\end{document}
